---
title       : mtcars dataset analysis
subtitle    : mpg and vairables (Cylinders, Transmission, Gears, Carburetors)
author      : M. Chitnis
job         : Developing Data Products course project
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlihter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Shiny App Input and Output

The Shiny App uses the mtcars dataset and allows user to select a variable to run a liner regression model.

To run the app:

Select the varible you want to run regression for from 
  1. Number of cylinders
  2. Transmission
  3. Gears
  4. Carburetors

Click Submit

--- 

## mtcars dataset

Motor Trend Car Road Tests : The data was extracted from the 1974 Motor Trend US magazine and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973–74 models).

A data frame with 32 observations on 11 variables

mpg: Miles/(US) gallon, cyl: Number of cylinders, disp: Displacement (cu.in.), hp: Gross horsepower,
drat: Rear axle ratio, wt: Weight (lb/1000), qsec: 1/4 mile time, vs: V/S, am: Transmission (0 = automatic, 1 = manual), gear: Number of forward gears, carb: Number of carburetors
          
Source: Henderson and Velleman (1981), Building multiple regression models interactively. Biometrics, 37, 391–411.

---

## Regression model summary
```{r}
l <- lm(mpg~cyl, data=mtcars)
summary(l)
```

---

## Regression model plot
```{r}
plot(l)
```